Non-kissing and non-crossing complexes \\ for gentle algebras

### 2018-07-02 draft/accordionComplexSurfaces.tex
definition curve

\begin{definition}
A \defn{marked surface}~$\bar\surface \eqdef (\surface, M)$ is an orientable surface~$\surface$ with boundaries, together with a set~$M$ of marked points which can be on the boundary of~$\surface$ or not.
For~$V \subset \surface$, a \defn{$V$-arc} on~$\bar\surface$ is a curve on~$\surface$ connecting two points of~$V$ and whose interior is disjoint from~$M$ and the boundary of~$\surface$.
As usual, arcs are considered up to homotopy relative to their endpoints in~$\surface \ssm M$, and curves homotopic to a boundary are not allowed.
Two arcs \defn{cross} when they intersect in~their~interior.
\end{definition}

@@

\subsection{Accordion complex, slalom complex, and non-crossing complex}
Let~$\bar\surface = (\surface, V \sqcup V\dual)$ be a surface with two disjoint sets~$V$ and~$V\dual$ of marked points, and let~$B$ be the corresponding blossom points.

\begin{definition}
A \defn{$B$-curve} is a curve on~$\surface$ which at each end either reaches a point of~$B$ or infinitely circles around and finally reaches a puncture of~$V \sqcup V\dual$.
Curves are considered up to homotopy relative to their endpoints in~$\surface \ssm (B \sqcup V \sqcup V\dual)$, and curves homotopic to a boundary are not allowed.
\end{definition}

%Let~$I$ denote the interior points and $B$ the blossom points.
We say that a $B$-arc is \defn{external} if it is homotopic to a boundary arc of~$\surface \ssm B$, and \defn{internal} otherwise.
Note that no $B$-arc can cross an external $B$-arc.
Consider two dual cellular dissections~$\dissection$ and~$\dissection\dual$ of~$\bar\surface$.

We will always assume that collections of arcs on a surface are in minimal position, in the sense that they cross each other transversaly, and the number of crossings is minimal.
This is always possible up to homotopy. \pierreguy{Reference?}
With this assumption, each segment of a~$B$-arc that lies in a face~$f$ of the dissection~$\dissection$ has two intersection points (called crossings) with the edges of~$f$.
Note that the edges of~$f$ may be on the boundary of the surface.

\begin{definition}
\label{def:accordion}
A \defn{$\dissection$-accordion} is a $B$-arc~$\alpha$ of~$\bar\surface$ such that whenever~$\alpha$ crosses a face~$f$ of~$\dissection$,
\begin{itemize}
\item the two edges~$e_1$ and~$e_2$ of~$f$ crossed by~$\alpha$ are adjacent on the boundary of~$f$,
\item $\alpha$, $e_1$ and~$e_2$ bound a disk inside~$f$ that does not contain~$f\dual{}$.
\end{itemize}
\end{definition}

>>>>

\begin{definition}
A \defn{marked surface}~$\bar\surface \eqdef (\surface, M)$ is an orientable surface~$\surface$ with boundaries, together with a set~$M$ of marked points which can be on the boundary of~$\surface$ or not.
For~$V \subset \surface$,
\begin{itemize}
\item a \defn{$V$-arc} on~$\bar\surface$ is a curve on~$\surface$ connecting two points of~$V$ and whose interior is disjoint from~$M$ and the boundary of~$\surface$.
\item a \defn{$V$-curve} on~$\bar\surface$ is a curve on~$\surface$ which at each end either reaches a point of~$V$ or infinitely circles around and finally reaches a puncture of~$M$.
\end{itemize}
As usual, curves and arcs are considered up to homotopy relative to their endpoints in~$\surface \ssm M$, and curves homotopic to a boundary are not allowed.
\end{definition}

\begin{definition}
Two curves or arcs \defn{cross} when they intersect in~their~interior.
We will always assume that collections of arcs on a surface are in minimal position, in the sense that they cross each other transversaly, and the number of crossings is minimal.
This is always possible up to homotopy. \pierreguy{Reference?}
\end{definition}

@@

\subsection{Accordion complex, slalom complex, and non-crossing complex}
Let~$\bar\surface = (\surface, V \sqcup V\dual)$ be a surface with two disjoint sets~$V$ and~$V\dual$ of marked points, and let~$B$ be the corresponding blossom points.
%
%\begin{definition}
%A \defn{$B$-curve} is a curve on~$\surface$ which at each end either reaches a point of~$B$ or infinitely circles around and finally reaches a puncture of~$V \sqcup V\dual$.
%Curves are considered up to homotopy relative to their endpoints in~$\surface \ssm (B \sqcup V \sqcup V\dual)$, and curves homotopic to a boundary are not allowed.
%\end{definition}
%
%Let~$I$ denote the interior points and $B$ the blossom points.
We say that a $B$-curve is \defn{external} if it is homotopic to a boundary arc of~$\surface \ssm B$, and \defn{internal} otherwise.
Note that no $B$-curve can cross an external $B$-arc.
Consider two dual cellular dissections~$\dissection$ and~$\dissection\dual$ of~$\bar\surface$.

%With this assumption, each segment of a~$B$-arc that lies in a face~$f$ of the dissection~$\dissection$ has two intersection points (called crossings) with the edges of~$f$.
%Note that the edges of~$f$ may be on the boundary of the surface.

\begin{definition}
\label{def:accordion}
A \defn{$\dissection$-accordion} is a $B$-curve~$\alpha$ of~$\bar\surface$ such that whenever~$\alpha$ meets a face~$f$~of~$\dissection$,
\begin{itemize}
\item it enters crossing an edge~$e_1$ and leaves crossing an edge~$e_2$ (in other words, $\alpha$ is not allowed to circle around~$f\dual$ when~$f\dual$ is a puncture),
\item the two edges~$e_1$ and~$e_2$ of~$f$ crossed by~$\alpha$ are adjacent on the boundary of~$f$,
\item $\alpha$, $e_1$ and~$e_2$ bound a disk inside~$f$ that does not contain~$f\dual{}$.
\end{itemize}
\end{definition}
